### 2016-12-15 Objects/Objects.tex
Object reco edit round 1

In this chapter the physics objects necessary to be able to perform searches with \Pgt leptons
in the final state, and how they are reconstructed in \ac{CMS}, will be discussed. The 
descriptions correspond to the algorithms as used during Run 2. Where there are differences
between the algorithms used in Run 1 and Run 2 this will be discussed at the end
of the relevant section. Section \ref{sec:objects_pv} discusses the algorithms
used to reconstruct charged tracks in the inner tracker, with section \ref{sec:objects_ele}
describing how these tracks are combined with \ac{ECAL} energy deposits to reconstruct electrons.
In section \ref{sec:objects_muo} the combination of charged tracks in the inner tracker with
hits in the muon chambers to form reconstructed muons will be discussed. Section \ref{sec:objects_pf}
describes the \ac{PF} algorithm, which uses information from all subdetectors in \ac{CMS} to reconstruct
all stable particles, which is of particular importance for the reconstruction of jets, missing transverse
energy and hadronic taus as discussed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
respectively.

\section{Tracks and vertices}
\label{sec:objects_pv}
To reconstruct the trajectories of charged particles, and therefore
their momenta and positions, from the hits these particles leave in the 
inner tracker, dedicated algorithms are required. In \ac{CMS} the
\ac{CTF} algorithm is used. This algorithm performs four steps:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item Initial estimates of the parameters of the trajectory are given by track seeds, providing track candidates found using hits in 2 or 3 layers of the inner tracker
\item The track seeds are extrapolated using a Kalman filter \cite{trk-kf}, which extrapolates the seeding trajectories along the expected flight path of a charged particle 
and adds additional matched hits it finds in the tracker layers to the track.
\item After the extrapolation has reached the final tracker layers, the Kalman filter is run again, now with the full set of hits that have been found in the previous step.
This provides the best estimate of the track parameters
\item Tracks that fail a specified set of quality criteria are rejected
\end{itemize}

@@

The reconstructed tracks are used to determine the positions of all interaction
vertices in the event. Primary vertices are reconstructed by clustering
tracks that appear to have originated from the same vertex, then fitting 
for the position of the vertex using the associated tracks. The tracks 
are clustered using the \ac{DA} algorithm \cite{vtx-da}, which identifies
the most probable vertex candidates and assigns tracks to them. Vertex
candidates with at least two associated tracks are fitted using an adaptive
vertex fitter \cite{vtx-adaptivefit} to obtain the best estimate
of the vertex position as well as an indicator for the success of the fit.
Each track is assigned a weight $w_i$ between 0 and 1 which reflects the probability
that it belongs to the vertex it is associated with. If the track is consistent
with the vertex position the weight will be closer to 1, if not the weight 
will be smaller. Using this the number of degrees of freedom in the fit
can be defined as
\begin{equation}\label{eqn:pv_ndof}
n_{\text{dof}} = -3 + 2 \Sigma_{i=1}^{Ntracks}w_i,
\end{equation}
which is strongly correlated with the number of tracks arising from the interaction region
and can therefore be used to select genuine interactions. For the analysis
presented in chapter \ref{chap:hhh}, which uses data collected during Run 1, to select the primary vertex, 
this variable
was required to be greater than 4, in addition to requirements on the distance between
the vertex and the nominal interaction point ($\Delta z < 24$ cm and $\Delta x-y < 2$ cm). 
The primary vertex was then taken as the vertex passing these quality criteria that 
had the largest scalar sum \pT of associated tracks. For the Run 2 analyses presented
later the quality requirements were removed and the primary vertex, the vertex
of the hard scattering process, is simply taken as the reconstructed vertex with
largest scalar sum \pT of associated tracks.
The resolution of the z--coordinate of the primary vertex was measured in
collisions at $\sqrt{s}=7$ TeV and depends strongly on the number of tracks
associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.

\begin{figure}
\begin{center}
\subfloat[Resolution in x]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResX.png}}
\subfloat[Resolution in z]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResZ.png}}
\end{center}
\caption{Resolution of the x-- (a) and z--coordinate  (b)
of reconstructed primary vertices
as a function of the scalar sum \pT of the tracks, 
measured for the 2015 running conditions in blue triangles
and for 2016 in red squares.
The resolution improves
with higher sum \pT (generally corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
\label{fig:objects_tracks_pvres}
\end{figure}

\section{Electrons}
\label{sec:objects_ele}
Electrons are reconstructed by combining tracks reconstructed
in the inner tracker with energy deposits in the \ac{ECAL} \cite{cms-elereco-run1}.
A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
described in section \ref{sec:objects_pf}. Because electrons lose on average 33-86\% of
their energy by radiating photons before the \ac{ECAL} is reached, depending on the thickness of
the intervening material. To accurately reconstruct the energy of the electron it is
important to catch the energies of photons, which are spread in the $\phi$ direction
due to the magnetic field. Therefore \textit{supercluster} algorithms are needed to perform
the clustering. In this approach the clustering
is done by defining a seed crystal as the one containg the most energy deposited
in a region being considered and having a certain minimum transverse energy.
In the barrel arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
to the cluster, stepping sideways in both directions in $\phi$, if this
array contains a minimum energy deposit. These clusters are grouped into 
superclusters if each distinct cluster has a seed array with a minimum energy deposit.
In the endcaps the clusters combined into superclusters are arrays of $5\times 5$ crystals,
merged into superclusters within a range in $\eta$ of $\pm 0.07$ and a range in $\phi$ of $\pm 0.3$ rad.

Because the electrons radiate bremsstrahlung photons in the tracker, the
change in electron track curvature is large. The reconstruction of these
tracks using the \ac{CTF} is compromised as a result of this, and 
therefore a dedicated tracking algorithm is used. For high \pT electrons
the best efficiency is reached by using an \ac{ECAL}-based track seeding
algorithm which extrapolates the position and energy of the supercluster
to the first layers of the tracker to determine rough areas to look for
tracker seeds in. Once the seeds have been determined they are extrapolated
and smoothed using the \ac{GSF} \cite{trk-gsf} instead of the Kalman Filter, which 
approximates the non-Gaussian energy loss in each layer by the combination of 
Gaussian distributions rather than the single Gaussian used in the Kalman filter.

@@

To be identified as an electron, a particle has to be reconstructed as
an electron by the \ac{PF} algorithm, and must in addition pass
more advanced identification criteria based on some of the variables used in the
standalone electron reconstruction, which provide separation power from backgrounds
such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
decays. Both cut--based and MVA--based algorithms are available. For the selection of electrons in 
the analyses presented in later chapters these MVA--based algorithms are usually used, 
with exceptions for the loose identification criteria required for veto-electrons. 
The variables used to train the electron identification BDT are:

\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
label of the $\eta$ and $\phi$ calorimeter cell. The circularity =  $1 -\frac{E1\times5}{E5\times5}$, with
$E1\times5$ and $E5\times5$ the energies in a $1\times5$ and a $5\times5$ grid around the super cluster seed,
respectively. Shape variable R9 = $\frac{E3\times3}{E_{SC}}$, with $E3\times3$ the energy in a $3\times3$ grid
of cells around the super cluster seed and $E_{SC}$ the raw energy of the super cluster.
\item The number of valid hits in the track fit, the $\chi^2$ of the track fit and the $\chi^2$ of the GSFTrack fit
\item The number of GSFtrack hits, the number of expected missing inner hits and the result of the conversion vertex fit
\item The distance $\Delta \eta$ and $\Delta \phi$ between the reconstructed super cluster and the associated track at the position of the primary vertex, and the distance in $\eta$ between the super cluster and the track at the calorimeter surface.
\item H/E, the ratio of the hadronic energy over the electromagnetic energy in the super cluster and E/P, the ratio of the super cluster energy over the momentum of the track associated with the electron
\item The ratio of the energy of the electron cluster and the momentum of the associated track, evaluated at the electron cluster,
 and $1/E_e - 1/P_e$, with $E_e$ the energy of the electron candidate and $P_e$ its momentum.
\end{itemize}

@@

\subsection{Isolation}
\label{sec:objects_ele_iso}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy--flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}, for the analyses presented
in later chapters a combined relative isolation variable is defined as:
\begin{equation}\label{eqn:electron_reliso}
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}(\text{charged}) + \mathrm{max}(\Sigma E_{\text{T}}(\text{neutral}) + \Sigma E_{\text{T}}(\text{photon}) - \Delta\beta \Sigma E_{\text{T}}(\text{PU}),0)}{P_{T}^{e}},
\end{equation}
Where the \pT and \ET sums are taken within a cone in $\eta - \phi$ around the direction
of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT of all charged \ac{PF} 
hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
the electron's axis. The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
run over all neutral hadronic energy and photon energy within the cone of radius $\Delta R$.
The contribution from neutral particles due to pile--up needs to be subtracted from
this term, which is estimated as the sum of charged hadronic \pT for hadrons not associated
with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$ \cite{SMHtautauCMS}.

\section{Muons}
\label{sec:objects_muo}
Muons are reconstructed by combining tracker tracks and tracks
from the muon system \cite{cms-muon-reco}. Two complementary approaches are used for this,
\textit{Global muon reconstruction} and \textit{tracker muon reconstruction}. The former starts from 
tracks reconstructed in the muon system and searches for a matching
tracker track, then re-applies the Kalman filter on the combination
of muon system and tracker hits. Conversely, the tracker muon reconstruction starts from
tracks in the inner tracker which pass requirements on momentum to be considered
a muon candidate track. The trajectory is then extrapolated to the muon systems and
considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs} is found.
Due to the requirement of a single muon segment this method is more efficeint than the global muon
reconstruction for muons with \pT smaller than 5 GeV \cite{cms-muon-reco}.
For muons with \pT greater than 200 GeV, the momentum resolution is improved
by the global muon reconstruction \cite{cms-muon-cosmics-perf}.

The muon momentum resolution was measured in p--p collisions at $\sqrt{s}=7$ TeV
for muons with \pT up to 100 GeV and found to range from 1--6\% depending
on detector region. For muons with \pT between 100 GeV and 1 TeV the momentum resolution
was determined to be better than 10\% in the barrel region using cosmic rays \cite{cms-muon-reco}.
%At values of the transverse momentum pT below about 200 GeV/c, the momentum resolution for a muon track is driven by measurements in the silicon tracker. As a particle’s momen- tum increases and the curvature of its corresponding track decreases, however, momentum resolution in the tracker becomes limited by position measurement resolution (including mis- alignment effects). One can then benefit from the large lever arm and 3.8 T magnetic field in the region between the tracker and the muon system by including hits in the muon chambers.

@@

For the analysis presented in chapter CHAPMSSM additional ``Medium'' muon requirements were made \cite{CMS-PAS-HIG-16-037}.
Apart from having passed either the global or tracker muon reconstruction, the fraction
of valid tracker hits must be greater than 49\%. Additional requirements are made on the
$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
position matching, on the kink finder in the inner tracker, and the segment compatibility. The segment
compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.
The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
is used as a discriminator. If the $\chi^2$ value is large, this could signal an in-flight decay.
The compatibility of the tracker- and standalone-reconstructed position is evaluated
by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
compatibility there.

To pass the identification, global- or tracker muons
with a large enough fraction of tracker hits must  \textbf{either} 
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The muon is reconstructed by the global muon reconstruction algorithm
\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
\item The segment compatibility is $>$ 0.303
\end{itemize}
\textit{or}:
\begin{itemize}
\item The segment compatibility is $>$ 0.451
\end{itemize}

In the analysis described in chapter \ref{chap:hhh}, where Run 1 data 
was used, muons were required to pass ``Tight'' identification requirements \cite{cms-muon-reco}. 
The criteria are
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The muon must be reconstructed by the global muon algorithm
\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
\item The global track fit must include hits from at least one chamber in the muon system
\item The inner tracker track must be matched to muon segments in at least two muon stations (ie the muon must be reconstructed as a tracker muon too)
\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
\end{itemize}

@@

The \ac{PF} algorithm starts from charged particle tracks measured
by the inner tracker, muon tracks measured in the muon system, and 
energy deposits in the calorimeters. These energy deposits are combined
using a clustering algorithm, so that stable neutral particles can be identified,
separated from charged hadrons, and electrons and all Bremsstrahlung photons
can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
\ac{ECAL} endcaps, first and second \ac{PS} layers, \ac{HCAL} barrel and \ac{HCAL} endcaps, with no 
clustering employed in the \ac{HF}.
%And to aid energy measurement of charged hadrons for which
%tracks were low quality, or high pT
The clustering algorithm used for \ac{PF} starts from \textit{cluster seeds},
calorimeter cells with local energy maxima. Topological clusters are built by 
merging neighbouring cells into the cluster, provided that the cells
being merged in contain a certain minimum energy.
The threshold is 800 MeV in the \ac{HCAL} and two standard deviations above the
expected noise level in the \ac{ECAL}, meaning 80 MeV in the barrel and up 
to 300 MeV in the endcaps. Cell energies can be shared between multiple
\ac{PF} clusters, depending on the distance between a cell and the centre of the cluster.

Any given particle will usually give rise to multiple \ac{PF}
elements in the different subdetectors. To provide full reconstruction
of each particle, and avoid double counting,  the next step in the
\ac{PF} algorithm is to link the different elements. This is
achieved by defining a distance parameter between any two \ac{PF} elements
in the event, which quantifies the link quality. Directly and indirectly
linked elements are considered as input blocks to the reconstruction and
identification algorithm. Links between charged tracks and calorimeter
clusters are established by extrapolating the track from its last measured
tracker hit to the \ac{PS} layers, the \ac{ECAL} and the \ac{HCAL}. %in ECAL to expected maximum of a 
%typical longitudinal electron shower profile and in the HCAL at a depth correspnding to one interaction
%length.
If the extrapolated track position is within the boundaries of the cluster, plus the size
of one cell in each direction to account for gaps between cells and multiple scattering, the
track is said to be linked to the calorimeter cluster. The distance is taken as the distance $\Delta R$ 
between the position of the cluster and the position of the track. Tangents to tracks are also extrapolated
to the ECAL from the track--tracker layer interaction points, and clusters can be 
linked to the track as a possible Bremsstrahlung photon if the extrapolated tangent
position is within the boundaries of the cluster.
Links between calorimeter clusters are made when the cluster position in the
more granular calorimeter is within the cluster of the less granular calorimeter,
with the link distance again defined as the $\Delta R$ between two cluster positions.
To determine links between charged tracks in the inner tracker and a muon track
in the muon system, a global fit between the two tracks is performed, where the link
is accepted if requirements on the maximum $\chi^2$ of this fit are met. This
$\chi^2$ also determines the distance parameter.

For each block, particles are identified following a sequence
of tests. First, if there is a link between a tracker track and a muon system track,
a particle flow muon is identified if the combined tracker and muon system
momentum is compatible with the tracker-only momentum. %within three standard deviations
The muon track is removed from the block before the next step of the algorithm.

>>>>

In this chapter the physics objects necessary to be able to perform searches with \Pgt leptons
in the final state, and how they are reconstructed in \ac{CMS}, will be discussed. Section \ref{sec:objects_pv} details the algorithms
used to reconstruct charged particle tracks in the inner tracker, with section \ref{sec:objects_ele}
describing how these tracks are combined with \ac{ECAL} energy deposits to reconstruct electrons.
In section \ref{sec:objects_muo} the combination of charged tracks in the inner tracker with
hits in the muon chambers to form reconstructed muons will be discussed. Section \ref{sec:objects_pf}
describes the \ac{PF} algorithm, which uses information from all subdetectors in \ac{CMS} to reconstruct
all stable particles, which is of particular importance for the reconstruction of jets, missing transverse
energy and hadronic taus as discussed in sections \ref{sec:objects_jets}, \ref{sec:objects_met} and \ref{sec:objects_tau} 
respectively.

\section{Tracks and vertices}
\label{sec:objects_pv}
To reconstruct the trajectories of charged particles - and therefore
their momenta and positions - from the hits these particles leave in the 
inner tracker, dedicated algorithms are required. In \ac{CMS} the
\ac{CTF} algorithm is used. This algorithm performs four steps:
First, initial estimates of the parameters of the trajectory are given by track seeds, 
made out of hits found in 2 or 3 layers of the inner tracker. Then, the track seeds
are extrapolated using a \ac{KF} \cite{trk-kf}, which extrapolates the seeding
trajectories along the expected flight path of a charged particle and adds 
additional matched hits it finds in the tracker layers it traverses to the track.
After the extrapolation has reached the final tracker layers, the \ac{KF} is run again,
now with the full set of hits that have been found in the previous step. This provides the best
estimate of the track parameters. Finally, tracks that fail a specified set of quality 
criteria are rejected.

@@

The reconstructed tracks are used to determine the positions of all interaction
vertices in the event. Primary vertices are reconstructed by clustering
tracks that appear to have originated from the same vertex, then fitting 
for the position of the vertex using the associated tracks. The clustering 
is performed using the \ac{DA} algorithm \cite{vtx-da}, which identifies
the most probable vertex candidates and assigns tracks to them. Vertex
candidates with at least two associated tracks are fitted using an adaptive
vertex fitter \cite{vtx-adaptivefit} to determine the best estimate of the 
vertex position. The analyses presented in CHAPMSSM take the primary
vertex of the hard scatter as the reconstructed vertex with largest scalar sum \pT~of
the associated tracks. This differs from the analysis presented in chapter \ref{chap:hhh},
where requirements on the quality of the vertex
fit and the distances between the vertex and the nominal interaction point 
were made.
 %By doing this both the best estimate
%of the vertex position and an indicator for the success of the fit are obtained.
%Each track is assigned a weight $w_i$ between 0 and 1, where values 
%closer to 1 indicate more consistency with the vertex position.
%The number of degrees of freedom in the fit can then be defined as
%\begin{equation}\label{eqn:pv_ndof}
%n_{\text{dof}} = -3 + 2 \Sigma_{i=1}^{Ntracks}w_i,
%\end{equation}
%which is strongly correlated with the number of tracks arising from the interaction region
%and can therefore be used to select genuine interactions. During Run 1 this variable was
%used in many analyses, including the one presented in chapter \ref{chap:hhh}, to define
%good--quality primary vertices. In addition to requiring $n_{\text{dof}}>4$, the distances
%between the vertex and the nominal interaction point were required
%to be $\Delta z< 24$ cm and $\Delta xy < 2$ cm. The primary vertex of the
%hard scatter was then taken as the vertex with greatest scalar sum \pT~ of associated
%tracks that passed these requirements. For the analyses with data from Run 2 the
%quality requirements were removed and the primary vertex of the hard scatter was simply taken
%as the reconstructed vertex with largest scalar sum \pT~ of tracks.

The resolution of the x-- and z--coordinates of the primary vertex were measured in
collisions at $\sqrt{s}=13$ TeV and depend strongly on the number of tracks
associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.

\begin{figure}
\begin{center}
\subfloat[Resolution in x]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResX.png}}
\subfloat[Resolution in z]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResZ.png}}
\end{center}
\caption{Resolution of the x-- (a) and z--coordinate  (b)
of reconstructed primary vertices
as a function of the scalar sum \pT of the tracks, 
measured for the 2015 running conditions in blue triangles
and for 2016 in red squares.
The resolution improves
with higher sum \pT (corresponding to larger numbers of tracks) \cite{cms-trk-dp}.}
\label{fig:objects_tracks_pvres}
\end{figure}

\section{Electrons}
\label{sec:objects_ele}
Electrons are reconstructed by combining tracks reconstructed
in the inner tracker with energy deposits in the \ac{ECAL} \cite{cms-elereco-run1}.
A standalone electron reconstruction algorithm \cite{cms-elereco-run1} complements the \ac{PF} approach
described in section \ref{sec:objects_pf}.
Depending on the thickness of the intervening material, electrons lose up to 86 \% of their energy on
average by radiating photons before the \ac{ECAL} is reached.
To accurately reconstruct the energy of the electron it is
important to catch the energies of bremsstrahlung photons, which are spread in the $\phi$ direction
due to the magnetic field. Therefore ``supercluster'' algorithms are needed.
In these algorithms the clustering
is performed by defining a seed crystal as the crystal containg the most deposited energy
in a region under consideration, where the transverse energy in this crystal
passes a minimum threshold.
In the barrel, arrays of $5\times 1$ crystals in $\eta \times \phi$ are then added
to the cluster, stepping sideways in both directions in $\phi$. The array is
only added to the cluster if the energy deposited in it passes a threshold.
These clusters are grouped into superclusters if each distinct cluster has a seed array in 
which the energy deposit is larger than a pre-defined minimum.
In the endcaps the clusters combined into superclusters are arrays of $5\times 5$ crystals,
merged into superclusters within a range in $\eta$ of $\pm 0.07$ and a range in $\phi$ of $\pm 0.3$ rad.

Due to the radiation of bremsstrahlung photons in the tracker,
the change in electron track curvature can be large, and so the \ac{CTF} does
not perform optimally. Therefore a dedicated tracking algorithm is used.
For high \pT~electrons, the best efficiency is reached
by the use of an \ac{ECAL}-based track seeding algorithm
which extrapolates the position and energy of the supercluster to the first
layers of the tracker to determine the rough area where the tracker seeds should be.
Once the tracker seeds have been determined they are extrapolated
and smoothed using the \ac{GSF} \cite{trk-gsf} instead of the \ac{KF}, which 
approximates the non-Gaussian energy loss in each layer by the combination of 
Gaussian distributions rather than the single Gaussian used in the \ac{KF}.

@@

For a particle to be identified as an electron, it 
has to be reconstructed as an electron by the \ac{PF} algorithm, 
and must in addition pass more advanced identification criteria based on some of the variables used in the
standalone electron reconstruction, which provide separation power from backgrounds
such as photon conversions, jets misidentified as electrons, or electrons from b- and c-quark
decays. Both cut--based and MVA--based algorithms are available. For the selection of electrons in 
the analyses presented in later chapters these MVA--based algorithms are usually used, 
with exceptions for the loose identification criteria required for veto-electrons. 
This BDT is trained using variables such as:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item Cluster shape variables, such as $\sigma_{i\eta,i\eta}$, the energy-weighted width in units of $\eta$ crystals. 
\item Track quality variables
\item Distances in $\eta$ and $\phi$ betaween the supercluster and the associated track
\item Ratios between hadronic and electromagnetic energy in the region of the supercluster, between supercluster energy and momentum of the track, and including 
$1/E_{\text{SC}} - 1/p_{\Pe}$, the inverse of the supercluster energy, with the inverse of electron track momentum subtracted
%\item Cluster shape variables $\sigma_{i\eta,i\eta}$ and $\sigma_{i\phi,i\phi}$, with $i\eta$ and $i\phi$ the integer
%label of the $\eta$ and $\phi$ calorimeter cell. The circularity =  $1 -\frac{E1\times5}{E5\times5}$, with
%$E1\times5$ and $E5\times5$ the energies in a $1\times5$ and a $5\times5$ grid around the super cluster seed,
%respectively. Shape variable R9 = $\frac{E3\times3}{E_{SC}}$, with $E3\times3$ the energy in a $3\times3$ grid
%of cells around the super cluster seed and $E_{SC}$ the raw energy of the super cluster.
%\item The number of valid hits in the track fit, the $\chi^2$ of the track fit and the $\chi^2$ of the GSFTrack fit
%%\item The number of GSFtrack hits, the number of expected missing inner hits and the result of the conversion vertex fit
%\item The distance $\Delta \eta$ and $\Delta \phi$ between the reconstructed super cluster and the associated track at the position of the primary vertex, and the distance in $\eta$ between the super cluster and the track at the calorimeter surface.
%\item H/E, the ratio of the hadronic energy over the electromagnetic energy in the super cluster and E/P, the ratio of the super cluster energy over the momentum of the track associated with the electron
%\item The ratio of the energy of the electron cluster and the momentum of the associated track, evaluated at the electron cluster,
% and $1/E_e - 1/P_e$, with $E_e$ the energy of the electron candidate and $P_e$ its momentum.
\end{itemize}

@@

\subsection{Isolation}
\label{sec:objects_ele_iso}
The identification requirements discussed up to now reduce the backgrounds 
from misidentified electrons, but do not eliminate them completely. If jets are
misidentified as electrons, or an electron resulting from a heavy--flavour 
decay is identified, the electron is not isolated. Therefore requirements
on the electron isolation can reduce these backgrounds even further.
Different isolation definitions are used in \ac{CMS}, for the analyses presented
in later chapters a combined relative isolation variable is defined as \cite{SMHtautauCMS}:
\begin{equation}\label{eqn:electron_reliso}
I_{\text{rel}} = \frac{\Sigma p_{\text{T}}^{\text{charged})} + \mathrm{max}(\Sigma E_{\text{T}}^{\text{neutral}} + \Sigma E_{\text{T}}^{\text{photon}} - \Delta\beta \Sigma E_{\text{T}}^{\text{PU}},0)}{P_{T}^{e}},
\end{equation}
Where the \pT~and \ET~sums are taken within a cone in $\eta - \phi$ around the direction
of the electron, $\Delta R = 0.4$ during Run 1 and $\Delta R = 0.3$ during Run 2 \cite{CMS-PAS-HIG-16-037}.
The sum over \pT$^{\text{charged}}$ corresponds to the \pT~of all charged \ac{PF} 
hadrons associated with the primary vertex and within the cone of radius $\Delta R$ around
the electron's axis. The \ET$^{\text{neutral}}$ and \ET$^{\text{photon}}$ sums
run over all neutral hadronic energy and photon energy within the cone of radius $\Delta R$.
The contribution from neutral particles due to pile--up needs to be subtracted from
this term, which is estimated as the sum of charged hadronic \pT~for hadrons not associated
with the primary vertex, multiplied by a $\Delta \beta$ factor of $\frac{1}{2}$ \cite{SMHtautauCMS}.

\section{Muons}
\label{sec:objects_muo}
Muons are reconstructed by combining tracker tracks and tracks
from the muon system \cite{cms-muon-reco}. Two complementary approaches are used,
\textit{global muon reconstruction} and \textit{tracker muon reconstruction}. The former starts from 
tracks reconstructed in the muon system and searches for a matching
tracker track, then re--applies the \ac{KF} on the combination
of muon system and tracker hits. Conversely, the tracker muon reconstruction starts from
tracks in the inner tracker which pass requirements on momentum to be considered
a muon candidate track. The trajectory is then extrapolated to the muon systems and
considered a muon if at least one muon segment, a track stub in the \ac{DT} or \ac{CSCs} is found.
Due to the requirement of a single muon segment this method is more efficient than the global muon
reconstruction for muons with \pT~smaller than 5 GeV \cite{cms-muon-reco}.
For muons with \pT~greater than 200 GeV, the momentum resolution is improved
by the global muon reconstruction \cite{cms-muon-cosmics-perf}.

The muon momentum resolution was measured in p--p collisions at $\sqrt{s}=7$ TeV
for muons with \pT~up to 100 GeV and found to range from 1--6\% depending
on detector region. For muons with \pT~between 100 GeV and 1 TeV the momentum resolution
was determined to be better than 10\% in the barrel region using cosmic rays \cite{cms-muon-reco}.
%At values of the transverse momentum pT below about 200 GeV/c, the momentum resolution for a muon track is driven by measurements in the silicon tracker. As a particle’s momen- tum increases and the curvature of its corresponding track decreases, however, momentum resolution in the tracker becomes limited by position measurement resolution (including mis- alignment effects). One can then benefit from the large lever arm and 3.8 T magnetic field in the region between the tracker and the muon system by including hits in the muon chambers.

@@

For the analysis presented in chapter CHAPMSSM additional ``medium'' muon requirements were made \cite{CMS-PAS-HIG-16-037}.
Apart from having passed either the global or tracker muon reconstruction, the fraction
of valid tracker hits must be greater than 49\%. Additional requirements are made on the
$\chi^2$/$N_{\text{dof}}$ of the global track fit, on the compatibility of the tracker- and standalone-reconstructed
position matching, on the kink finder in the inner tracker, and the segment compatibility. 
The compatibility of the tracker- and standalone-reconstructed position is evaluated
by extrapolating both the muon track and the tracker track to the same surface and evaluating the $\chi^2$ 
compatibility there.
The kink finder determines the $\chi^2$ compatibility between the positions of the outward- and inward interpolated
tracks in each layer of the inner tracker. The largest $\chi^2$ value found at any of the tracker layers 
is used as a discriminator. If the $\chi^2$ value is large, this could signal an in-flight decay.
The segment
compatibility is a weight between 0 and 1 which is a measure of the compatibility of a track with
the muon track segments in muon stations it has crossed. Numbers closer to 1 represent
a greater compatibility of the track with the muon segments, and therefore with the track belonging to a muon.

To pass the identification, global- or tracker muons
with a large enough fraction of tracker hits must pass \textbf{either} 
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The muon is reconstructed by the global muon reconstruction algorithm
\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit, using both the tracker and muon system hits, should be less than 3
\item The $\chi^2$ compatibility of the tracker-standalone position is smaller than 12
\item The $\chi^2$ compatibility of the kink finder in the tracker is less than 20
\item The segment compatibility is $>$ 0.303
\end{itemize}
\textit{or}:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The segment compatibility is $>$ 0.451
\end{itemize}
In the analysis described in chapter \ref{chap:hhh}, where Run 1 data 
was used, muons were required to pass ``tight'' identification requirements \cite{cms-muon-reco}. 
The criteria are
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item The muon must be reconstructed by the global muon algorithm
\item The $\chi^2$/$N_{\text{dof}}$ of the global track fit must be smaller than 10
\item The global track fit must include hits from at least one chamber in the muon system
\item The inner tracker track must be matched to muon segments in at least two muon stations (which means the muon must also be reconstructed as a tracker muon)
\item The tracker track must have at least one hit in the pixel detector, and hits in ten tracker layers.
\end{itemize}

@@

The \ac{PF} algorithm starts from charged particle tracks measured
by the inner tracker, muon tracks measured in the muon system, and 
energy deposits in the calorimeters. These energy deposits are combined
using a clustering algorithm, so that stable neutral particles can be identified,
separated from charged hadrons, and electrons and all bremsstrahlung photons
can be reconstructed. Clustering is performed separately in the \ac{ECAL} barrel,
\ac{ECAL} endcaps, first and second \ac{PS} layers, \ac{HCAL} barrel and \ac{HCAL} endcaps, with no 
clustering employed in the \ac{HF}.
%And to aid energy measurement of charged hadrons for which
%tracks were low quality, or high pT
The clustering algorithm used for \ac{PF} starts from \textit{cluster seeds},
calorimeter cells with local energy maxima. Topological clusters are built by 
merging neighbouring cells into the cluster, provided that the cells
being merged in contain a certain minimum energy.
The threshold is 800 MeV in the \ac{HCAL} and two standard deviations above the
expected noise level in the \ac{ECAL}, meaning 80 MeV in the barrel and up 
to 300 MeV in the endcaps. Cell energies can be shared between multiple
\ac{PF} clusters, depending on the distance between a cell and the centre of the cluster.

Any given particle will usually give rise to multiple \ac{PF}
elements in the different subdetectors. To provide full reconstruction
of each particle, and avoid double counting,  the next step in the
\ac{PF} algorithm is to link the different elements. This is
achieved by defining a distance parameter between any two \ac{PF} elements
in the event, which quantifies the link quality. Directly and indirectly
linked elements are considered as input blocks to the reconstruction and
identification algorithm. Links between charged tracks and calorimeter
clusters are established by extrapolating the track from its last measured
tracker hit to the \ac{PS} layers, the \ac{ECAL} and the \ac{HCAL}. %in ECAL to expected maximum of a 
%typical longitudinal electron shower profile and in the HCAL at a depth correspnding to one interaction
%length.
If the extrapolated track position is within the boundaries of the cluster, plus the size
of one cell in each direction to account for gaps between cells and multiple scattering, the
track is said to be linked to the calorimeter cluster. The distance is taken as the distance $\Delta R$ 
between the position of the cluster and the position of the track. Tangents to tracks are also extrapolated
to the ECAL from the track--tracker layer interaction points, and clusters can be 
linked to the track as a possible bremsstrahlung photon if the extrapolated tangent
position is within the boundaries of the cluster.
Links between calorimeter clusters are made when the cluster position in the
more granular calorimeter is within the cluster of the less granular calorimeter,
with the link distance again defined as the $\Delta R$ between two cluster positions.
To determine links between charged tracks in the inner tracker and a muon track
in the muon system, a global fit between the two tracks is performed, where the link
is accepted if requirements on the maximum $\chi^2$ of this fit are met. This
$\chi^2$ also determines the distance parameter.

For each block, particles are identified following a sequence
of tests. First, if there is a link between a tracker track and a muon system track,
a \ac{PF} muon is identified if the combined tracker and muon system
momentum is compatible with the tracker-only momentum. %within three standard deviations
The muon track is removed from the block before the next step of the algorithm.
